Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-22 paper.tex
added subsection about L

@@

In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast
ADT, then
\[
  \evalEqv{\effCEK{C}}{\ineffCEKD}
\]
The main work of the proof is in a lemma that establishes a weak
bisimulation between \effCEK{C} and \ineffCEKD{}.  The bisimulation
goes more smoothly if we require two more properties of the cast
representation: that the casts form a monoid (the $id$ and $seq$
operators) and that the cast constructor is equivalent to the identity
operator when applied to an identical source and target type.
However, the final theorem does not require these two properties
because we can prove 1) that \effCEK{C_1} and \effCEK{C_2} are
equivalent for any two Lazy D Cast ADTs $C_1$ and $C_2$, and 2) there
is an instance of the Lazy D Cast ADT, named $L$, that is a monoid and
satisfies the two extra properties, and is therefore equivalent to
\ineffCEKD{}. So by transitivity, for any Lazy D Cast ADT $C$ we have
\evalEqv{\effCEK{C}}{\ineffCEKD}.

@@

@@

\begin{theorem}[\lazyD{} hypercoercion Respect \ineffCEKD]
	if $\judgetype{\emptyset}{e}{T}$ and $o : T$
	\[
	\text{\evalEqv{\ineffCEKD}{\effCEK{H}}}
	\]
\end{theorem}
\begin{proof}
	Immediately from Theorem~\ref{thm:surely-lazyD-correct} and 
	Lemma~\ref{thm:hc-surely-lazyD}.
	Alternatively, from Lemma~\ref{thm:surely-monoidic-eval},
	Lemma~\ref{thm:hc-surely-lazyD}, and 
	Proposition~\ref{thm:hc-monoid}.
\end{proof}

>>>>

\todo[inline]{Jeremy needs to add text. -JS}

@@

In this subsection, we prove that for all $C$, if $C$ is a Lazy D Cast
ADT, then
\[
  \evalEqv{\effCEK{C}}{\ineffCEKD}
\]
The main work of the proof is in a lemma that establishes a weak
bisimulation between \effCEK{C} and \ineffCEKD{}.  The bisimulation
goes more smoothly if we require two more properties of the cast
representation: that the casts form a monoid (the $id$ and $seq$
operators) and that the cast constructor is equivalent to the identity
operator when applied to an identical source and target type.
However, the final theorem does not require these two properties
because we can prove 1) that \effCEK{C_1} and \effCEK{C_2} are
equivalent for any two Lazy D Cast ADTs $C_1$ and $C_2$
(Proposition~\ref{thm:surely-lazyD-eqv}), and 2) there is an instance
of the Lazy D Cast ADT, named $L$, that is a monoid and satisfies the
two extra properties, and is therefore equivalent to \ineffCEKD{}
(Lemma~\ref{lem:L-correct}). So by transitivity, for any Lazy D Cast
ADT $C$ we have \evalEqv{\effCEK{C}}{\ineffCEKD}.

@@

\subsubsection{The $L$ instance of the Lazy D Cast ADT}

\todo[inline]{KC, please add the definition of $L$ -JS}

\begin{proposition}[$L$ properties]\ 
  \begin{enumerate}
  \item $L$ is an instance of the Lazy D ADT
  \item $L$ is a monoid
  \item $cast(T,l,T) = id(T)$
  \end{enumerate}
\end{proposition}

\begin{lemma}[$L$ is correct wrt. \ineffCEKD]
  \label{lem:L-correct}
  \[
  \text{\evalEqv{\effCEK{L}}{\ineffCEKD}}
  \]
\end{lemma}

@@

\begin{theorem}[\lazyD{} hypercoercion Respect \ineffCEKD]
  If $\judgetype{\emptyset}{e}{T}$ and $o : T$
  \[
  \text{\evalEqv{\effCEK{H}}{\ineffCEKD}}
  \]
\end{theorem}
\begin{proof}
	Immediately from Theorem~\ref{thm:surely-lazyD-correct} and 
	Lemma~\ref{thm:hc-surely-lazyD}.
	Alternatively, from Lemma~\ref{thm:surely-monoidic-eval},
	Lemma~\ref{thm:hc-surely-lazyD}, and 
	Proposition~\ref{thm:hc-monoid}.
\end{proof}
